\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-11 implementation.tex
.

@@

% more scalable 
\subsection{Search Parameters}

The search parameters for PWA-Rel include the parameters of S3CAM:
$N$, $\epsilon$ and $\Delta$. Additionally, they also include the
maximum error budget $\delta_{max}$ for OLS and the maximum length of
segmented trajectory for building $k$-relational models.

The effects of $N$, $\epsilon$ and $\Delta$
on S3CAM's performance were detailed in~\cite{zutshi2014multiple}. However, they also have an effect on
relational modeling. A finer grid with small cells produces more
accurate models than a coarser grid with large cells. Similarly,
small time length trajectory segments result in more accurate
modeling.
%An increase in the number of samples can increases the
%accuracy of regression.

\paragraph{Maximum Model Error ($\boldsymbol{\delta}_{\bold{max}}$) .}
Given a $\delta_{max}$, we keep increasing $k$ during the
$k$-relational modeling process till $\delta_i \le \delta_{max}$ is
satisfied. A $k_{max}$ is introduced to bound the longest
segmented trajectory which can be considered.

\subsection{Reasons for Failure}
The approach can fail to find a counter-example, even when it exists, in
one of three ways.

\begin{itemize}

    \item \emph{S3CAM Fails}: No abstract counter-example is found by
        S3CAM. We can remedy it by increasing search budgets and/or
        restarting.

    \item \emph{BMC Fails}: An abstract counter-example is found, but
        the BMC fails to find a concrete counter-example in the PWA
        relational model. The failure can be attributed to either (a)
        a spurious abstract counter-examples or (b) a poorly estimated
        model. The former can be addressed by restarting but the
        latter requires that the maximum model error $\delta_{max}$ be
        decreased.

    \item \emph{Inaccurate PWA Modeling}: An abstract counter-example
        is found, and it is successfully concretized in the PWA
        relational model by the BMC. However, it is not reproducible
        in the black box system. This happens when the PWA relational
        model is not precise enough.
\end{itemize}

>>>>

\mypara{The search parameters} for PWA-Rel include the parameters of
S3CAM: $N$, $\epsilon$ and $\Delta$. Additionally, they also include
the maximum error budget $\delta_{max}$ for OLS and the maximum length
of segmented trajectory for building $k$-relational models.  The
effects of $N$, $\epsilon$ and $\Delta$ on S3CAM's performance were
detailed in~\cite{zutshi2014multiple}. However, they also have an
effect on relational modeling. A finer grid with small cells produces
more accurate models than a coarser grid with large cells. Similarly,
small time length trajectory segments result in more accurate
modeling.

%An increase in the number of samples can increases the
%accuracy of regression.

% \paragraph{Maximum Model Error ($\boldsymbol{\delta}_{\bold{max}}$) .}
% Given a $\delta_{max}$, we keep increasing $k$ during the
% $k$-relational modeling process till $\delta_i \le \delta_{max}$ is
% satisfied. A $k_{max}$ is introduced to bound the longest
% segmented trajectory which can be considered.

@@

\subsection{Reasons for Failure}

The approach can fail to find a counter-example, even when it exists,
in one of three ways. As it is dependant on S3CAM to find abstract
paths, it can fail when (a) S3CAM fails to find abstract
counter-examples. We can remedy it by increasing search budgets and/or
restarting. Even when abstract counter-examples are found, they may
not be \emph{concretizable}. In such a case, the (b) BMC search fails.
The failure can be attributed to either spurious abstract
counter-examples or a poorly estimated model. The former can be
addressed by restarting but the latter requires that the maximum model
error $\delta_{max}$ be decreased. Finally, the (c) counter-example
from the BMC might not be reproducible in the black box system. This
happens if the relational model is not precise enough.
